Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores with time series modeling

### 2020-01-06 Ben_Manuscripts/stochastic_transport/Draft.tex
added clarifying comment
Comments from Shirts.

%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
and Predicts Long Timescale Behavior in Nanoscale Pores.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux in macroscopic length pores. With our first model, based on 
  the anomalous diffusion theory, we show how solute dynamics can be modeled 
  as a fractional diffusion process subordinate to a continuous time random 
  walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. Our second model, a generalization of Markov state models,
  treats the configurational state of the system as a Markov process, each of
  which has state dependent transport behavior. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that our models reasonably reproduce
  the MSDs calculated from MD simulations. Finally, we demonstrate how one can
  use our models in order to calculate flux of a given solute across a 
  macroscopic-length pore and, based on those quantities, the membrane's selectivity
  towards each solute. Overall, this work helps connect the relationship between
  microscopic chemically-dependent solute motions and macroscopic membrane performance.

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to 
  % have the potential to disrupt
  conventional membrane separation techniques by being selective based not only on solute
  size and charge, but on solute chemical functionality as well.~\cite{dischinger_application_2017}
  One can tune the functionality of LLC monomers
  in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two types of LLC membranes are in active development. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.

  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

  In our previous work, we used molecular dynamics (MD) simulations to study the transport
  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
  The H\textsubscript{II} phase is a simpler geometry to model than the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs, however they would be of greater value to a wider audience if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux and selectivity. Due to the size of the types of systems we are studying (at least 62,000 atoms)
  it is prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

@@

  %BJC4: Tried to make this paragraph connect to previous a little better
  Using a bottom-up modeling approach, we can parameterize single particle behavior
  by reducing our MD simulations to observations of several key properties
  that have the greatest influence on solute dynamics and then construct an ensemble 
  of characteristic single solute trajectories useful for making long timescale
  predictions with computational ease and lower uncertainties. Fortunately, there 
  is an abundance of information encoded in the complex solute trajectories. Into a
  model, we can incorporate fluctuations and time-dependent correlations in solute
  position as well as the length of time solutes are trapped. We can add further
  detail by integrating our time series analysis with our knowledge of the primary
  trapping mechanisms as well as the solute's changing chemical environment within
  the heterogeneous membrane.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

@@

  Where applicable, the sFBM model is an elegant way to characterize single 
  particle trajectories and in addition to providing an easy and efficient way to 
  simulate solute trajectories, can help uncover the underlying solute-membrane
  interactions which result in observed transport mechanisms. It can help 
  researchers formulate hypotheses to explain why a certain set of parameters is
  characteristic to a specific solute. This is largely the approach we used to
  discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model.

@@

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on one's research goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  Finally, we use both models in order to predict solute flux and selectivity in 
  pores of macroscopic length, thus achieving a better understanding
  of macroscopic properties on the basis of microscopic dynamics. We show that 
  anti-correlated solute hopping behavior severely reduces flux relative to 
  uncorrelated behavior. We use the relative solute fluxes to calculate the 
  membrane's selectivity between all pairs of solutes and demonstrate that, when 
  solutes display different degrees of anti-correlated hopping behavior, selectivity
  becomes a function of pore length. With this improved understanding of 
  macroscopic behavior, we can begin to think more critically about how to design 
  membranes in order to selectively pass or reject specific solutes.

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018.  %BJC4: version 2018. That's it not 2018.3 or anything. 
  ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
  We performed all post-simulation trajectory analysis using python scripts which 
  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate scripts to use for subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the distal tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

@@

  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, but instead it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
  MSD is given by:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation} 
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  One can characterize the CTRW component of an sFBM process by the parameters which describe
  its dwell time and hop length distributions. We used the \texttt{ruptures} python
  package in order to automatically identify mean shifts in solute trajectories, 
  indicating hops.\cite{truong_ruptures:_2018} We used the corresponding hop lengths
  and dwell times between hops to construct empirical distributions.

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We cannot
  observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha_d$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha_d, \lambda) = n(1 - \alpha_d)\ln\lambda - n\ln\Gamma(1 - \alpha_d, t_{min}\lambda) - \alpha_d\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 0.5 ns time lags of the 
  empirically measured autocorrelation function.

  \subsubsection{Subordinated Fractional L\'evy Motion}\label{method:sflm}

>>>>

%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
%MRS6: I would focus first on the outputs.  Not sure about the behavior/vs. selectivity.  Probably 
% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the titel
%\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
%and Predicts Long Timescale Behavior in Nanoscale Pores.}
\title{Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores
with time series modeling}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux,
  %MRS6: added
  and thus solute selectivity, 
  in macroscopic length pores. 
  %MRS6: tweak
  %With our first model, based on the 
  First, using
  anomalous diffusion theory, we show how solute dynamics can be modeled 
  as a fractional diffusion process subordinate to a continuous time random 
  walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. 
  %MRS6: tweak.

  Next, we generalize Markov state models,
  treating the configurational state of the system as a Markov process, each 
  %MRS6: tweak
  %of which has state dependent transport behavior. 
  state of which has separate transport properties
  For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that our models reasonably reproduce
  the MSDs calculated from MD simulations.

  Finally, we demonstrate how one can
  use our models 
  %in order to calculate 
  to estimate
  flux of a 
  %given 
  solute across a 
  macroscopic-length pore and, based on those quantities, the membrane's selectivity
  towards each solute. Overall, this work helps to connect 
  % the relationship between
  microscopic chemically-dependent solute motions and macroscopic membrane performance.

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to 
  % have the potential to disrupt
  conventional membrane separation techniques by being selective based not only on solute
  size and charge, but on solute chemical functionality as well.~\cite{dischinger_application_2017}
  One can tune the functionality of LLC monomers
  in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Tweaks.
  Two
  general types of LLC membranes 
  are 
  being actively developed.
  %in active development. 
  The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.

  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied experimentally in membrane applications.
  %MRS6: should these references be contracted?
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

  In our previous work, we used molecular dynamics (MD) simulations to study the transport
  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
  The H\textsubscript{II} phase is a simpler geometry to model than the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs
  %MRS6: breaking sentence.
  However, they would be of greater value to a 
  %wider audience 
  larger set of reseachers
  if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux and selectivity. Due to the size of the types of systems we are studying (at least 62,000 atoms)
  it is prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). 
  %MRS:deleting.
  %And 
  Even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

@@

  %BJC4: Tried to make this paragraph connect to previous a little better
  Using a bottom-up modeling approach, we can parameterize single particle behavior
  by 
  %MRS6:
  extracting from 
  %reducing
  our MD simulations 
  %to observations of several key 
  properties
  of their trajectories
  that have the greatest influence on solute dynamics and then construct an ensemble 
  of characteristic single solute trajectories 
  with these properties
  useful for making long timescale
  predictions with computational ease and lower uncertainties. Fortunately, there 
  is an abundance of information encoded in the complex solute trajectories. Into a
  model, we can incorporate fluctuations and time-dependent correlations in solute
  position as well as the length of time solutes are trapped. We can add further
  detail by integrating our time series analysis with our knowledge of the primary
  trapping mechanisms as well as the solute's changing chemical environment within
  the heterogeneous membrane.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. 
  %MRS6: maybe rephrase the next - 'dive' is kind of casual?  Also, it seems more like the start of the next paragraph.
  The formulation
  of these models requires a dive into stochastically driven processes.

@@

  Where applicable, the sFBM model is an elegant way to characterize single 
  particle trajectories and in addition to providing an easy and efficient way to 
  simulate solute trajectories, can help uncover the underlying solute-membrane
  interactions which result in observed transport mechanisms. It can help 
  researchers formulate hypotheses to explain why a certain set of parameters is
  characteristic to a specific solute. 
  %MRS6: next sentence implies you used sFBM to uncover the mechanisms of the last paper, but that detail wasn't really there? 
  This is largely the approach we used to
  discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model.

@@

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on 
  %MRS:
  %one's research
  a give reseach study's
  goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  Finally, we use both models in order to predict solute flux and selectivity in 
  pores of macroscopic length, thus achieving a better understanding
  of macroscopic properties on the basis of microscopic dynamics. We show that 
  anti-correlated solute hopping behavior severely reduces flux relative to 
  uncorrelated behavior. We use the relative solute fluxes to 
  %MRS6: tweak
  %calculate 
  estimate
  the 
  membrane's selectivity between all pairs of solutes and demonstrate that, when 
  solutes display different degrees of anti-correlated hopping behavior, selectivity
  becomes a function of pore length. With this improved understanding of 
  macroscopic behavior, we can begin to think more critically about how to design 
  membranes in order to selectively pass or reject specific solutes.

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.  %BJC4: version 2018. That's it not 2018.3 or anything. 
  We performed all post-simulation trajectory analysis using Python scripts which 
  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate scripts to use for subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the 
  %MRS6: isn't distal tail redundant? 
  distal tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

@@

  Solutes in this system 
  %MRS6: added
  very clearly 
  exhibit 
  subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, but instead it follows a power law of the form:
  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  %MRS6: next paragraph could be clearer.  Maybe motivate at the beginning why the importance of time. vs. ensemble averated. It's sprung a sort of a surprise there's a difference 
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
  MSD is given by:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation} 
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. 
  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
  Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  One can characterize the CTRW component of an sFBM process by the parameters which describe
  its dwell time and hop length distributions. We used the \texttt{ruptures} Python
  package in order to automatically identify mean shifts in solute trajectories, 
  indicating hops.\cite{truong_ruptures:_2018} We used the corresponding hop lengths
  and dwell times between hops to construct empirical distributions.

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We cannot
  observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha_d$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha_d, \lambda) = n(1 - \alpha_d)\ln\lambda - n\ln\Gamma(1 - \alpha_d, t_{min}\lambda) - \alpha_d\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten  
  0.5 ns time lags of the 
  empirically measured autocorrelation function.

  \subsubsection{Subordinated Fractional L\'evy Motion}\label{method:sflm}
  %MRS6: maybe make it clearer that this is something you will be doing in the paper 
  Since we also want to account for the possibility that
  %If the 
  distribution of hops is not Gaussian, we can model them with the
  more general class of L\'evy stable distributions. For independent and identically
  distributed random variables, the generalized central limit theorem assures 
  convergence of the associated probability distribution function (PDF) to a 
  L\'evy stable PDF. \cite{klages_anomalous_2008} The characteristic equation which 
  describes the Fourier transform of a L\'evy stable PDF is:
  %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
  \begin{equation}
    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
  \end{equation}
  where \\
  \[\omega(k, \alpha_h) = \begin{cases}
  	\tan{\frac{\pi \alpha_h}{2}} & \text{if}~\alpha_h \neq 1, 0 < \alpha_h < 2, \\
  	-\frac{2}{\pi}\ln |k| & \text{if}~\alpha_h = 1
  	 \end{cases}
  \]
  $\alpha_h$ is the index of stability or L\'evy index, $\beta$ is the skewness 
  parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
  familiar case, and one of three that can be expressed in terms of elementary functions,
  is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
  centered about 0 implying that $\beta$ and $\mu$ are both 0.
